### 2014-11-01 paper/experiments.tex
fix some issues

We conducted several performance tests to measure the throughput and scalability of our system. All these tests were performed in an LAN system called Lattice which has a network bandwidth of 1Gbps. All nodes are Intel(R) Xeon(R) 2.4GHz 4 core duo machines with 1 Gbp of memory. Sample code used for all tests can be found here\cite{solutionCode}.

\subsection{Inter node communication}
We used a graph as shown in Figure \ref{ecgGraph} to process ECG signal data. For our solution and Yahoo S4\cite{neumeyer2010s4} EventProducer reads a file contains over 7500000 ecg records and push events with multiple threads. Twitter Storm\cite{twitterStorm} does not allow user threads to push data. So we used the Spout thread to send messages into the system. EventReceiver  receives the ECG events, process them and calculate heart rate interval periodically.  
We execute our system with 1, 2 and 4  EventReceivers for each system and measured the throughput, load average and network bandwidth  for each case. Throughput was measured at the EventProducer calculating total time required to send messages and the total number of messages send. Load average and network bandwidth were measured using top and atop linux commands respectively. Figure \ref{throuput} shows the throughput variation with the number of nodes for all systems.

@@

As shown in the Figure \ref{throuput} our solution out performs Twitter storm\cite{twitterStorm} and Yahoo S4\cite{neumeyer2010s4}. However by looking the Figure \ref{throuput} one might think even our system does not scalable although it perform high. In order to examine the reason behind this we need to look into the network bandwidth and CPU load average values.

@@

After measuring the throughput we examined the  total amount of extra bytes each system sends to transfer the information from EventProducer to EventReceiver. Our ECGEvent has two double fields called time and value (ecg signal value) and a streamID which is a 4 byte string. So we calculated total bytes to send this information as 20 bytes (16 for two double and 4 for streamID). Then by using the throughput and the bandwidth usage of the system we calculate the total number of bytes each system uses at network layer to send this message. By reducing 20 information bytes we can calculate the over head bytes for each system. Figure \ref{efficiency} compares these numbers.

@@

        \caption{Efficiency of Message serialization}
        \label{efficiency}
\end{figure}

As shown in the figure \ref{efficiency} Twitter storm\cite{twitterStorm} uses a minimum over head while Yahoo S4\cite{neumeyer2010s4} performs badly compared to other two. This overhead is due to its usage of  java serializations to serialize data. Then we analyzed to which our solution spends extra 32 bytes. Our solution adds a sequence number (an integer), receiving process id (a 8 byte string for this scenario), sending process id (a 8 byte string for this scenario) to order messages, dispatch the message to correct process and to parse the message at the server. Altogether it adds 26 (serialization format of a string uses two more bytes to keep the string length) extra bytes to each message at application level and other 4 bytes due to tcp over head. This is the trade off we had to pay for improve the parallelism compared to direct one tcp communication per process.

@@

%\begin{figure}
%        \centering
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{throughputs.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{networkps.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{networks.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{loadaverages.png}
%        \end{subfigure}
%        \caption{Scalability of the System}
%        \label{scalability}
%\end{figure}

>>>>

We conducted several performance tests to measure the throughput and scalability of our system. All these tests were performed in an LAN system called Lattice which has a network bandwidth of 1Gbps. All nodes are Intel(R) Xeon(R) 2.4GHz 4 core duo machines with 1 Gbp of memory. We used Apache S4 0.6.0 verson and Apache storm 0.9.2 version. Sample code used for all tests can be found here\cite{solutionCode}.

\subsection{Inter node communication}
We used a graph as shown in Figure \ref{ecgGraph} to process ECG signal data. Our solution and Yahoo S4\cite{neumeyer2010s4} EventProducer reads a file containing over 7500000 ecg records and push events with multiple threads. Twitter Storm\cite{twitterStorm} does not allow user threads to push data. So we used the Spout thread to send messages into the system. EventReceiver  receives the ECG events, process them and calculate heart rate interval periodically.  
\subsubsection{Throughput}
We execute our system with 1, 2 and 4  EventReceivers for each system and measured the throughput, load average and network bandwidth  for each case. Throughput was measured at the EventProducer calculating total time required to send messages and the total number of messages send. Load average and network bandwidth were measured using top and atop linux commands respectively. Figure \ref{throuput} shows the throughput variation with the number of nodes for all systems.

@@

As shown in the Figure \ref{throuput} our solution out performs Twitter storm\cite{twitterStorm} and Yahoo S4\cite{neumeyer2010s4}. However by looking the Figure \ref{throuput} one might think even our solution does not scalable although it perform high. In order to examine the reason behind this we looked into the network bandwidth and CPU load average values.

@@

\subsubsection{Efficiency of Message Serialization}
After measuring the throughput we examined the  total amount of extra bytes each system sends to transfer the information from EventProducer to EventReceiver. Our ECGEvent has two double fields called time and value (ecg signal value) and a streamID which is a 4 byte string. So we calculated total bytes to send this information as 20 bytes (16 for two doubles and 4 for streamID). Then by using the throughput and the bandwidth usage of the system we calculated the total number of bytes each system uses at network layer to send this message. By reducing 20 information bytes we can calculate the over head bytes for each system. Figure \ref{efficiency} compares these numbers.

@@

        \caption{Efficiency of Message Serialization}
        \label{efficiency}
\end{figure}

As shown in the figure \ref{efficiency} Twitter storm\cite{twitterStorm} uses a minimum over head while Yahoo S4\cite{neumeyer2010s4} performs badly compared to other two. This overhead is due to its usage of  java serializations to serialize data. Then we analyzed for what our solution spends extra 32 bytes. Our solution adds a sequence number (an integer), receiving process id (a 8 byte string for this scenario), sending process id (a 8 byte string for this scenario) to order messages, dispatch the message to correct process and to parse the message at the server. Altogether it adds 26 (serialization format of a string uses two more bytes to keep the string length) extra bytes to each message at application level and other 4 bytes due to tcp over head. This is the trade off we had to pay to improve the parallelism compared to direct one tcp communication per process.

\subsubsection{Latency}
We examined the message latency between the event producer and receiver. For this experiment we send the time stamp at the producer along the message and calculated the latency at the receiver. We took 3000 samples over experiment duration. As shown in the figure \ref{latancydis}, we could calculate the mean latency as 221.86 with the 95\% confidence interval of (218.18, 225.55).

\begin{figure*}[!t]
        \centering
        \subfloat[Histogram]{\includegraphics[width=3.0in]{latencyHistogram.png}}
        \hfil
        \subfloat[Box Plot]{\includegraphics[width=3.0in]{latencyBoxPlot.png}}
        \caption{Message Latency Distribution}
        \label{latancydis}
\end{figure*}

@@
